\newcommand{\stSmalltalkSubtitle}
{a programming language\\
  purely \textbf{object oriented}\\
  and a \textbf{dynamic} environment}

\newcommand{\stSmalltalkConceptsTerm}{Smalltalk important concepts}
\newcommand{\stSmalltalkConceptsDefinition} {Smalltalk is an
  \emph{object-oriented}, \emph{dynamically-typed} language, with a
simple syntax which can be learnt in \emph{fifteen minutes}.
Its main advantage comes from the fact that it is \emph{very consistent}:

\begin{itemize}
\item everything is an object: classes, methods, numbers, etc.
\item a small number of rules, and no exceptions!
\end{itemize}

Smalltalk runs in a \emph{virtual machine}.  Development
takes place in an \emph{image} in which all objects live and are 
modified.}

\newcommand{\stSmalltalkSyntaxTerm}{Smalltalk syntax}
\newcommand{\stReservedWordsTerm}{Reserved words}
\newcommand{\stReservedCaractersTerm}{Reserved characters}

\newcommand{\stMessageSendingTerm}{Message sending}
\newcommand{\stMessageSendingDefinition}
{A method is called by sending a message to an object, the message receiver; the message returns an object. The message is based on natural language, having a subject, a verb and complements.
There are three message types: unary, binary and keyword.}

\newcommand{\stUnaryMessagesTerm}{Unary messages.}
\newcommand{\stUnaryMessagesDefinition}
{A unary message is one with no arguments.

\begin{displaycode}
array := Array new.

array size.
\end{displaycode}

The first example creates and returns a new instance of the Array
class, by sending it the message \code{new}. The second example asks for
the size of this array which returns \code{0}.}

\newcommand{\stBinaryMessagesTerm}{Binary messages.}
\newcommand{\stBinaryMessagesDefinition}{A binary message takes only
  one argument, is named by a symbol and is often used for arithmetic
  expressions.

\begin{displaycode}
3 + 4.

'Hello', ' World'.
\end{displaycode}

The \code{+} message is sent to the object \code{3} with \code{4} as a parameter. In the second case, the message \code{,} is sent to the string \code{'Hello'} with \code{' World'} as a parameter.}

\newcommand{\stKeywordMessagesTerm}{Keyword messages.}
\newcommand{\stKeywordMessagesDefinition}
{
  A keyword message can take one or more arguments. The arguments are inserted between each keyword, after each colon.

\begin{displaycode}
'Smalltalk' allButFirst: 5.

3 to: 10 by: 2.
\end{displaycode}

The first example calls the method \code{allButFirst:} on a string and
pass the argument \code{5}. The method returns the string
\code{'talk'}. The second example returns a collection containing
elements \code{3}, \code{5}, \code{7} and \code{9}.
}

\newcommand{\stDevelopmentEnvironmentTerm}{Development environment}
\newcommand{\stDevelopmentEnvironmentDefinition} {Most 
  Smalltalk implementations come with an integrated development
  environment that allows you to browse the source code and
  to interact with objects. Lots of tools are available, all
  implemented in Smalltalk thanks to a reflection API:

\begin{itemize}
\item a class and method browser;
\item refactoring tools;
\item object inspectors;
\item a debugger;
\item release management and version control tools;
\item and much, much more!
\end{itemize}

Code can be inspected and evaluated directly in the image, using simple key combinations and full menus.  }

\newcommand{\stImplementationTerm}{Implementations}
\newcommand{\stImplementationDefinition}
{
There are a number of Smalltalk implementations available:
\begin{description}
\item[Squeak:] free, open-source and multi-platform
  implementation. Actively developed by an international community.
\item[Visual Works:] proprietary and multi-platform, freely available
  for non commercial use.
\item[Gemstone:] proprietary implementation which includes an highly
  efficient object database.
\item[And others:] GNU Smalltalk, Smalltalk/X, SyX, VA Smalltalk, Dolphin\dots
\end{description}
}

\newcommand{\stSqueakCodeBrowserTerm}{The Squeak code browser}

\newcommand{\stApplicationsTerm}{Applications}
\newcommand{\stApplicationsDefinition}
{
Since its creation in the early 1980s, Smalltalk has been widely used in 
academic research as well as in commercial applications.  Here are some current Smalltalk
applications that are advancing the state of software.
\begin{description}
\item[Teaching:] EToys (Squeak), SqueakBot, BotsInc, Scratch\dots
\item[Multimedia:] Sophie, OpenCroquet, Plopp\dots
\item[Web development:] Seaside, Aida, Komanche, Swazoo\dots
\item[Persistence management:] object oriented databases (Magma, GemStone), relational databases (MySQL, PostgreSQL), object relational mapping (Glorp).
\end{description}
}

\newcommand{\stPloppDrawingSessionTerm}{A Plopp drawing session}

\newcommand{\stImageTerm}{Image}
\newcommand{\stImageDefinition}
{The Smalltalk environment contains a persistent object store, the
  image. This contains application code (classes and methods), objects
  holding application state and can even include the development
  tools to inspect and debug the program while it is executing.}

\newcommand{\stVMTerm}{Virtual Machine}
\newcommand{\stVMDefinition}
{A virtual machine is a program which is capable of executing other
  programs. It eases application portability.}

\newcommand{\stReflexionTerm}{Reflection}
\newcommand{\stReflexionDefinition} {A language is said to be reflective when
  it contains mechanisms to inspect and modify code during a program
  execution.}

\newcommand{\stDynamicTypingTerm}{Dynamic typing}
\newcommand{\stDynamicTypingDefinition} {Some languages force
  the developer to indicate the type of each variable (integer,
  string\dots); this is called static typing. Dynamic typing
does not impose this constraint, and so makes programs more reusable and easier to change.}

\newcommand{\stBooksTerm}{Books}
\newcommand{\stBooksDefinition}
{
\begin{itemize}
\item Numerous free books:\\
  \url{http://stephane.ducasse.free.fr/Books.html}

\item Smalltalk in general
  \begin{itemize}
  \item \emph{Smalltalk with Style}\\
		(Edward Klimas, Suzanne Skublics and
    David A. Thomas, free)
  \item \emph{Smalltalk by Example: the Developer's Guide} --
		(Alec Sharp, free)
  \end{itemize}

\item Squeak in particular
  \begin{itemize}
  \item \emph{Squeak by Example} -- (2007, free)
  \item \emph{Powerful Ideas in the Classroom}\\
		(BJ Allen-Conn and Kim Rose)
  \end{itemize}
\end{itemize}
}

\newcommand{\stSmalltalkActionsTerm}{Events}
\newcommand{\stSmalltalkActionsDefinition}
{
\begin{itemize}
\item European Smalltalk User Group conferences (ESUG). Since 1993, industrial and academic Smalltalkers meet in an European country.\\
  \url{http://www.esug.org/conferences}
\item Annual conference, organised in North America by the STIC (\url{http://www.stic.st}), an association with industrial actors and Smalltalk editors.\\
  \url{http://www.smalltalksolutions.com/}
\end{itemize}
}

\newcommand{\stInternetWebsitesDefinition}
{
\begin{itemize}
\item Official Squeak website:\\ \url{http://www.squeak.org}
\item Wiki:\\ \url{http://wiki.squeak.org}
\item News:\\ \url{http://news.squeak.org}
\end{itemize}
}

\newcommand{\stNilDefinition}{undefined object (default variable values)}
\newcommand{\stTrueAndFalseDefinition}{boolean objects}
\newcommand{\stSelfDefinition}{current object}
\newcommand{\stSuperDefinition}{current object in the super class context}
\newcommand{\stThisContextDefinition}{run-time stack of the current method}
\newcommand{\stAssignmentOperatorDefinition}{assignment}
\newcommand{\stReturnOperatorDefinition}{return a result from a method}
\newcommand{\stTempsDeclarationOperatorDefinition}{declaration of three  temporary variables}
\newcommand{\stDollarOperatorForCharacterADefinition}{character \code{a}}
\newcommand{\stLiteralArrayDefinition}{array containing two literals: the symbol \code{\#abc} and the number \code{123}}
\newcommand{\stDotOperatorDefinition}{terminate expressions}
\newcommand{\stSemiColonOperatorDefinition}{message cascade}
\newcommand{\stBlockOperatorDefinition}{code block (it's an object !)}

\newcommand{\stPeriodTerm}{period}
\newcommand{\stCommentTerm}{comment}
\newcommand{\stStringTerm}{string}

\newcommand{\stGlossaryTerm}{Glossary}

\newcommand{\stAndTerm}{and}
\newcommand{\stOrTerm}{or}

\newcommand{\stBlockTerm}{Block}
\newcommand{\stBlockDefinition}{

  Blocks are objects containing code that is not executed immediately.
  They are the basis for control structures like conditionals or
  loops.  Also, blocks can be used to attach behavior, e.g., to menu
  items.

  \begin{displaycode}
    \#('Hello ' 'World')

    \hspace{1cm}  do: [:string | Transcript show: string].
  \end{displaycode}

  The example sends the message \code{do:} to an array of strings with
  a block as a parameter. The block is evaluated once for each element
  in the array. The block parameter \code{string} contains each
  element of the array, one after the other. As a result of the whole
  expression, the strings \code{'Hello '} then \code{'World'} are
  displayed in the transcript.
   
}

\newcommand{\stSqueakCodeBrowserSize}{.75}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\seaSubtitle}{The framework for developing sophisticated
  web applications in Smalltalk}

%%% Local Variables:
%%% coding: utf-8-unix
%%% mode: latex
%%% TeX-master: "../flyer"
%%% TeX-PDF-mode: t
%%% ispell-local-dictionary: "english"
%%% End:

